---
title: "R Markdown Practice"
author: "Dr. S P Naik"
output:
  html_document: default
  latex_engine: xelatex
  pdf_document:
header-includes:
  - |
    \usepackage{fvextra}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{breaklines,commandchars=\\\{\}}
---

```{r setup, include=FALSE}
# Global wrapping for all code and printed output
knitr::opts_chunk$set(tidy = TRUE, tidy.opts = list(width.cutoff = 80))
options(width = 80)
```


# Hello World!
## Heading 2
### Heading 3
#### Heading 4
##### Heading 5

*italic*  
**Bold**

# **Hello World!**

1. List Item 1
2. List Item 2

- Bullet 1
- Bullet 2

You can type whatever you want in here and when you click "knit", it shall compile and produce the document. 
  
You can also add link to the text. For example, Dr S P Naik profile is available at **[Google Scholar](https://scholar.google.com/citations?user=zsSyZVoAAAAJ&hl=en&oi=ao)**

R Markdown allows the insertion of R code
```{r}
print("Hello world!")

#Assignment Operators and Basic Algebra in R
a=15
b=3
cat("Sum of a+b =", a+b)
cat("Difference of a-b =", a-b)
print(paste("Product of a*b =", a*b))

library(glue) #using the glue library
print(glue("Ratio of a÷b = {a/b}"))

#Playing with datasets
data=mtcars
data

## For better display

### Option 1 
library(kableExtra)

#### For html
#kable(mtcars,caption="Table 1: Motor Car Road Tests") %>% kable_styling(bootstrap_options = c("stripped","hover","condensed"))

### For pdf
#kable(mtcars,booktabs=TRUE, caption = "Table 1: Motor Car Road Tests") %>% kable_styling(latex_options = "hold_position")

library(gt)
data %>% gt() %>% tab_header(title = "Table 1: Motor Car Road Tests",subtitle = "A dataset of 32 cars from 1974")

```
  
Now let's move on to the next chunk of code.  

# **Plots with R for dataset mtcars**  
```{r}
library(ggplot2)

#Scatterplot for Mileage vs Weight
ggplot(data,aes(x=hp,y=mpg))+geom_point(col="darkgreen",pch=19, size=2)+ggtitle("Scatterplot: Mileage vs Power",subtitle = "Motor Trend Car Road Tests (1974)")+xlab("Power(in hp)")+ylab("Miles per gallon(mpg)")


```
  

**Note: Session Info**  
```{r}
sessionInfo()
```


